Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-23 sec_results.tex
adopted jasper's comment to Sec3

Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the relative pseudorapidity ($\Delta \eta$) and azimuthal angle ($\Delta \varphi$) differences between the trigger and associated particles. The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}. The left panel is for the 0--0.1\% multiplicity class. The right one is from the minimum bias events (0--100\% multiplicity class). The ridge structure is clearly observed in the high multiplicity class compared to the minimum-bias events while it is not seen in the minimum bias events. The away side is dominant from the correlation of back to back jet.

@@

 Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class(0--100\%) and the high multiplicity class (0--0.1\%). The near-side($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all the transverse momentum ranges studied while there is no hint of signal in the minimum bias class. The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class. The measurements in the high multiplicity class are compared with the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}. The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties. The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances. The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity. The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$. However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range. $\pythiam$ does not show any peaks in the near-side as expected and slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, which mainly come from the back to back jet correlations.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0-0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
	\label{fig:PlotDeltaPhi}
\end{figure}

The ridge yields as a function of  the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}. The particle multiplicity in this analysis is estimated with the forward subsystem(V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$. By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%. Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other. The spectrum is also compared with model calculations. $\pythiam$ gives zero yields since it does not contain the ridge effect. $\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the data as $\pttrigassoc$ increases.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.89\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box. The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line). }
	\label{fig:PlotYSpect}
\end{figure}

\subsection{Event scale dependent ridge yield}
The event scale dependent ridge yields are measured with the minimum $\ptlead=9.0$ (left) or $\ptjet=10.0$~ GeV/$c$ (right) thresholds for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection. In Fig.~\ref{fig:PlotCorrHMTSel}, The ridge structure still persist even with both selections. With the minimum $\ptjet$ selection, the correlations function has double peaks on the $\Delta\eta$ at $\Delta\varphi = \pi$ due to the requirement of the limited jet acceptance.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.pdf} }
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection. The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$. The minimum requirement for $\ptlead$ or $\ptjet$ is 9 and 10 GeV/$c$, respectively. }
	\label{fig:PlotCorrHMTSel}
\end{figure}

Projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$(lower) and $\ptjet$(upper) are shown in Fig.~\ref{fig:PlotDeltaPhiESE}. The near-side yield increases as requiring higher $\ptlead$ or $\ptjet$ from the yield in unbiased events, which is shown in the upper left panel. The Model calculations by $\pythiashoving$ and $\pythiam$ are shown with a blue and a orange line, respectively. The $\pythiashoving$ gives qualitative agreement of the near-side peak with the event scale selections. On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections. Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.

@@

The ridge yields as functions of the minimum $\ptlead$(left) and $\ptjet$(right) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}. The ridge yield increases with the increasing selection requirement.$\pythiashoving$ underestimates the ridge yield with the increasing event scale selection. $\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.

@@

>>>>

@@

Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the $\Delta \eta$ and $\Delta \varphi$ between the trigger and associated particles. The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}. The left panel is for the 0--0.1\% multiplicity class. The right one is from the minimum bias events (0--100\% multiplicity class). The ridge structure is clearly observed in the high multiplicity class while it is not seen in the minimum bias events. The away side is dominant from the correlation of back to back jet.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0-0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
	\label{fig:PlotDeltaPhi}
\end{figure}

Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high multiplicity class (0--0.1\%). The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of signal in the minimum bias class. The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class. The measurements in the high multiplicity class are compared with the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}. The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties. The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances. The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity. The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$. However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range. $\pythiam$ does not show any peaks in the near-side as expected and slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, which mainly come from the back to back jet correlations.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.90\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared with the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box. The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line). }
	\label{fig:PlotYSpect}
\end{figure}

The ridge yields as a function of  the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}. The particle multiplicity in this analysis is estimated with the forward subsystem (V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$. By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%. Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other. The spectrum is also compared with model calculations. $\pythiam$ gives zero yields since it does not contain the ridge effect. $\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the data as $\pttrigassoc$ increases.

\subsection{Event scale dependent ridge yield}
\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.pdf} }
	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection. The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$. The minimum requirement for $\ptlead$ or $\ptjet$ is 9 and 10 GeV/$c$, respectively. }
	\label{fig:PlotCorrHMTSel}
\end{figure}

Two-particle correlation functions as functions of the $\Delta \eta$ and $\Delta \varphi$ is also studied with two different event selections. As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure still persist with the minimum $\ptlead=9.0$ (left) or $\ptjet=10.0$~ GeV/$c$ (right) thresholds for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection.
With the minimum $\ptjet$ selection, the correlations function has double peaks on the $\Delta\eta$ at $\Delta\varphi = \pi$ due to the requirement of the limited jet acceptance.

@@

Projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) are shown in Fig.~\ref{fig:PlotDeltaPhiESE}. The near-side yield increases for higher $\ptlead$ or $\ptjet$ requirement compared to the yield in unbiased events. The results are compared to
$\pythiashoving$ and $\pythiam$ calculations. The $\pythiashoving$ gives qualitative agreement of the near-side peak with the event scale selections. On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections. Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.

@@

Finally, the ridge yields as functions of the minimum $\ptlead$ (left) and $\ptjet$ (right) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}. The ridge yield increases with increasing selection requirement. $\pythiashoving$ underestimates the ridge yield with the increasing event scale selection. $\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.

### 2020-06-23 sec_summary.tex
adopted jasper's comment to Sec3

\section{Conclusions}
\label{sec:summary}

The $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider. The spectrum of the ridge yield is measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class. The result is compared with CMS measurement and shown that the results are compatible. The PYTHIA8 string shoving quantitatively estimates the spectrum while PYTHIA8 default shows zero yield. Further understandings of the correlations in small system are attempted by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$. The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases. The results have been compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.

>>>>

\section{Conclusions}
\label{sec:summary}
Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV at the Large Hadron Collider. These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class. 
The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
%In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
PYTHIA8 string shoving quantitatively estimates the spectrum while $\pythiam$ shows zero yield. Further the ridge yields are studied in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$. The ridge structure still persist with both selections. The ridge yield with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases. The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
